### 2017-11-27 Docs/Thesis/docs/chapter3.tex
thesis update

%3nd-review
In this chapter, we will present our tool which aims to fill the gaps addressed in the chapter ~\ref{ch:introduction}. It is called SIMITAR (SnIffing, ModellIng and TrAffic geneRation) and aims to generate a platform-agnostic traffic: it can be extended to almost any traffic engine, including traffic generators tools and APIs. SIMITAR creates a  model in XML, configured using actual traces (from \textit{pcaps} or real-time sniffing), we call Compact Trace Descritor (CTD).

@@

% cycle of operation
%2nd-review
\begin{figure*}[ht!]
        \centering
        \includegraphics[height=3.0in]{figures/ch3/digram-project-cycle}
        \caption{This figure represents an operation cycle of SIMITAR, emphasizing each main step: sniffing, flow classification, data storing, data processing and fitting, model parameterization,  and synthetic traffic generation.}
    \label{fig:cycle-of-operation}
\end{figure*}

@@

To meet the requirements presented in the section ~\ref{ch:introduction}, we will present a solution, and define how each part works, as in a low-level requirement list\cite{sommerville}. SIMITAR architecture is presented in the figure~\ref{fig:architecture}, and it is composed of for components: a \textit{Sniffer}, a \textit{SQLite database}, a \textit{TraceAnalyzer}, a \textit{FlowGenerator};  and a \textit{Network Traffic Generator}, as subsystem. We describe each part below.

@@

%2nd-review
This component collects network traffic data and classifies it into flows, storing stores in an SQLite database. It defines each flow by the same criteria used by SDN switches\cite{sdn-survey}, through header fields matches (Link Protocol, Network Protocol, Network Source Address, Network Destination Address, Transport Protocol, Transport Source Port, Transport Destination Port). It can work over a \textit{pcap} file or over an Ethernet interface.

@@

The first version of this component was implemented in Shell Script (Bash).  Tsahrk\footnote{\href{https://www.wireshark.org/docs/man-pages/tshark.html}{https://www.wireshark.org/docs/man-pages/tshark.html}} was used to extract header fields, and Awk to match the flows, and Sed/Awk to create the Sqlite queries. This version was too slow to operate in real time on Ethernet interfaces. On the other hand, was fast to implement, and enable the implementation of the other components, before this last version was released. The second and cuerrent version is implemented using Python. This version used Pyshark \footnote{\href{https://pypi.python.org/pypi/pyshark}{https://pypi.python.org/pypi/pyshark}} as sniffer library.

It has a data structure we developed called \textit{OrderedSet}. A set is a list of elements with no repetition but do not keep track of the insertion order. Our OrderedSet does. Also, it make use of a  64 bits hash function of the family FNV\footnote{The collision probability of a good 64 bits hash function in a table with 10000 items is about of $2.71e-12$.}. The listed header fields are inputs for a hash function, its value is set on the ordered set, and its order(index on the \textit{OrderedSet}) is returned. The index value is set as a packet flowID.

%c++ http://ideone.com/F0V42m
%2nd-review
As future improvements for this component, we propose a more efficient implementation in C++ and data visualization for the collected data. We discuss this in deeper details in the chapter~\ref{ch:conclusion}.

@@

The database stores the collected raw data  from the traces for further analysis. The \textit{Sniffer} and the \textit{TraceAnalyzer} components uses the database.  We choose an SQLite database, because according to its specifications\footnote{\href{https://www.sqlite.org/whentouse.html}{https://www.sqlite.org/whentouse.html}}, it fits well our porposes. It is simple and well-suitable for an amount of data smaller than terabytes. In the figure ~\ref{fig:simitar-database} we present the relational model of our database, which stores a set of features extracted from packets, along with the flowID calculated by the sniffer component.

@@

This module is the core of our project. It creates a trace model via the analysis of the collected data. We define here a Compact Trace Descriptor (CTD) as a human and machine readable file, which describes an original traffic trace trough a set of flows, each of them described by a set of parameters, like header information and analytical models.

Therefore, the Trace Analyze learns the features from raw data of traces (stored in the SQLite database) and write them in an XML file.  In the figure~\ref{fig:CTD-diagram} we show a directory diagram of a CDT file. It has many of many flow fields, and each one contains each parameter estimated.

%\begin{figure*}[!ht]
%    \centering
%    \begin{subfigure}[t]{0.45\textwidth}
%        \centering
%        \includegraphics[height=2.5in]{figures/03_compact_trace_descriptor_tree_structure}
%        \caption{caption}
%    \end{subfigure}%
%    ~ 
%    \begin{subfigure}[t]{0.45\textwidth}
%        \centering
%        \includegraphics[height=2.5in]{figures/03_compact_trace_descriptor_tree_structure_2}
%        \caption{caption}
%    \end{subfigure}
%    \caption{caption}
%    \label{fig:CTD-diagram}
%\end{figure*}
%height=2.5in
%

@@

%3nd-review
\subsubsection{Flow features}

Some features are unique per flow and can be directly measured from the data. They are:

@@

%3nd-review
\subsubsection{Inter Packet Times}

@@

To represent inter packet times, we adopt a simplified version of the Harpoon traffic model. A deep explanation of the original model can be found at \cite{harpoon-paper} and \cite{harpoon-validation}. Here, we will explain our simplified version, which is illustrated at figure~\ref{fig:modified-harpoon-model}.

Harpoon uses a definition of each level, based on the measurement of SYN and ACK TCP flags. It use TCP flags (SYN) to classify packets in different levels, named there file, session, and user level. We choose to estimate these values, based on inter-packet times only. The distinction is made based on the time delay between packets.

In our algorithm simplified version, we define (as Harpoon does) three different layers of data transference to model and control: file, session, and flow. For SIMITAR, a file is just a sequence of consecutive packets transmitted continuously, without large interruption of traffic. It can be, for example, packets transmitted downloading a file, of UDP packets of a connection or a single ICMP echo packet. The session-layer refers to a sequence of multiple files transmitted between a source and a destination, belonging to the same flow.  And the flow level refers to the conjunct of flows, as classified by the Sniffer.  Now, we explain SIMITAR operation on each layer. All contants and defaults mode of operation can be changed by command line options.

In the \textbf{flow layer} the \textit{TraceAnalyzer} loads the flow arrival times from the database, and calculates the inter-packet times within the flow context.

At the \textbf{session layer}, we use a deterministic approach for evaluating file tranference time and times between files: ON/OFF times sequence of packet trains. We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.  We develop an algorithm called \textit{calcOnOff} responsible for estimating these times. It also determines the number of packets and bytes transferred by each file. Since the ON times will serve as input for actual traffic generators, we defined a minimum acceptable time for on periods equals to 100 ms. ON times can be arbitrary smalls, and they could be incompatible with acceptable ON periods for traffic generators and in the case of just one packet, the ON time would be zero. So setting aminimum acceptable time solve these issues. The OFF times, on the other hand, are defined by the constant \texttt{session\_cut\_time} \footnote{In the code it is called \texttt{DataProcessor::m\_session\_cut\_time} }. If the time between packets of the same flow is larger than this, we consider it belonging to a different file, so it is a Session OFF time. In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} for the \texttt{session\_cut\_time}: 30 seconds. The control of ON/OFF periods in the traffic generation is made by the \textit{FlowGenerator} component \footnote{This control is made by the class \texttt{NetworkFlow}}.

%2nd-review
In the \textbf{file layer}, we model the inter-packet times at the file level. To estimate inter-packet times within files, we select all inter-packet times smaller than \texttt{session\_cut\_time}\footnote{In the code it is called\texttt{DataProcessor::m\_session\_cut\_time} }. All files within the same flow are considered to follow the same model. We delegate the control of the inter-packet times to the underlying workload engine tool. We ordered them, from the best to the worst. Currently, we are using eight different stochastic functions parameterizations. They are Weibull(linear regression), Normal(mean/standard deviation calculation), Exponential(mean and linear regression estimation), Pareto(linear regression and maximum likelihood), Cauchy(linear regression) and Constant(mean calculation). From those, Weibull, Pareto, and Cauchy are heavy-tailed functions, and therefore self-similar processes. But if the flow has less than 30 packets, just the constant model is evaluated. It is because numerical methods gave poor results if the data sample used is small. We sort these models according to the Akaike Information Criterion (AIC) as default\cite{sourcesonoff-paper}\cite{bic-aic-comparision}. We will enter in deeper details on this methodology on the chapter ~\ref{ch:modeling-evaluation}. The methodology of selection is presented in the figure~\ref{fig:model-parameterization}

%2nd-review
\begin{figure*}[ht!]
    \centering
    \includegraphics[height=0.9in]{figures/ch3/simitar-parametrization}
    \caption{Diagram of parameterization and model selection for inter-packet times and inter-file times.}
    \label{fig:model-parameterization}
\end{figure*}

%\begin{figure*}[ht!]
%    \centering
%    \includegraphics[height=4.0in]{figures/ch3/alg-paremeterization}
%    \caption{caption.}
%    \label{fig:harpoon-alg-times-estimator}
%\end{figure*}

@@

%2nd-review
Our approach for the packet size is much simpler. Since the majority of packet size distribution found on real measurements are bi-modal \cite{packet-distribution-model}\cite{sourcesonoff-paper}\cite{udp-flows-model}, we first sort all packet sizes of flow in two modes. We define a packet size mode cut value of 750 bytes, same value adopted by \cite{udp-flows-model}.

%2nd-review
We know how much packets each mode has, and then we fit a model for it. We use three stochastic models: constant, exponential and normal. Since self-similarity do not make sense for packet-sizes, we prefer to use just the simpler models. When there is no packet for a model, we set a flag NO\_MODEL, and when there is just a single packet we just use the constant model. Then calculate the BIC and AIC for each, but we decide to set the constant model as the first.

As is possible to see in many works \cite{packet-distribution-model} \cite{udp-flows-model}, since the standard deviation of each mode tends to be small, constant fittings use to give good approximations. Also, it is computationally cheaper for the traffic generated than the other models, since no calculation is a need for each packet sent. Since both AIC and BIC criteria always will select the constant model as the worst, we decide to ignore this

@@

%2nd-review
We first implemented it using the D-ITG API. But our Flow Generator can use any traffic generator with API, CLI or script interface as well. To easily expand this component, we use the design pattern factory. If the user wants to introduce support for a new traffic generator, he just has to expand the class \texttt{DummyFlow} and add the support on the method \texttt{make\_flow()} of the class \texttt{NetworkFlow}. We will discuss this deeper in the next section.

%2nd-review
This component works in two different layers according to the traffic generators classification introduced in the chapter ~\ref{ch:literature-review}: at the Flow level, and packet level, as presented in the figure ~\ref{fig:layers-workload-tools}.

@@

%2nd-review
At the flow level, it controls each flow using the algorithm at figure~\ref{alg-simplified-harpoon}. This algorithm basically handles the our model defined at the figure~\ref{fig:modified-harpoon-model}.

%2nd-review
It starts a \textit{thread} for each flow in the \textit{Compact Trace Descriptor}, then the thread sleeps its \texttt{start\_delay}. It is the time when the first flow packet was captured in the original capture. it then calls the underlying traffic generation method, passing to it the file ON time, number of packets and number of bytes to be sent (file size). Then it sleeps the next Session-OFF time from the stack until it ends. When the list of ON/OFF times is over, the thread ends. The thread scheduling/joining is implemented by the class \texttt{NetworkTrace} and its sleep/wake process by the class \texttt{DummyFlow}.

@@

%2nd-review
At the packet level, it must use the expanded class of the \texttt{DummyFlow}. In this level, the job of our tool is to configure the underlying engine, to send a file. Therefore it uses the \textit{getters} available, and the passed parameters, defined by the operation described in the previous session. The implementation of this level should follow the flowchart presented in the figure ~\ref{fig:alg-traffic-engine-config}.
Down below we present a simplistic code of how the D-ITG API can be used to generate packet-level traffic. We call this concept \textit{Flow Generation Programming} A more complex configuration is possible, but it serves to illustrate the procedure. Its API documentation is available at on D-ITG web-site \footnote{\href{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}}. 
\begin{minted}[frame=single,
               framesep=3mm,
               linenos=true,
               xleftmargin=21pt,
               tabsize=4,
               fontsize=\scriptsize, 
               breaklines=true]{c++}
void flowGenerate(const counter& flowId, const time_sec& onTime, const uint& npackets, const uint& nbytes,  const string& netInterface)
{
	char localhost[CHAR_BUFFER];
	string strCommand;
	char command[CHAR_BUFFER];
	uint i = 0;
	int rc = 0;
	getLocalIp("eth0", localhost);
	strCommand += " -t " + std::to_string(onTime); 
	strCommand += " -k " + std::to_string(nbytes / 1024);
	strCommand += " -a " + getHostIP();
	if (this->getTransportProtocol() == PROTOCOL__TCP)
		strCommand += " -T TCP -D ";
	else if (this->getTransportProtocol() == PROTOCOL__UDP)
		strCommand += " -T UDP ";
	else if (this->getTransportProtocol() == PROTOCOL__ICMP)
		strCommand += " -T ICMP ";
	for(;;i++)
	{	
		StochasticModelFit idtModel = this->getInterDepertureTimeModel(i);
		if(idtModel.modelName() == WEIBULL)
		{
			strCommand += " -W " + std::to_string(idtModel.param1()) + " " + std::to_string(idtModel.param2());
			break;
		}
		else if ( idtModel.modelName() == CONSTANT)
		{
			strCommand += " -C " + std::to_string(nbytes/(1024*onTime));
			break;
		}
	}
	strcpy(command, strCommand.c_str());
	rc = DITGsend(localhost, command); // it is not blocking
    usleep(onTime*10e6);
	if (rc != 0)
	{
		printf("\nDITGsend() return value was %d\n", rc);
		exit(EXIT_FAILURE);
	}
}
\end{minted}

>>>>

% ok1

In this chapter, we will present our tool which aims to fill the gaps addressed in the chapter ~\ref{ch:introduction}. It is called SIMITAR (SnIffing, ModellIng and TrAffic geneRation) and aims to generate a platform-agnostic traffic: it can use as traffic generator engine almost any traffic generator tools and programming API. It just requires a programming or command line interface. SIMITAR creates a  model in XML based on actual traces (\textit{pcaps} or real-time captures), we call Compact Trace Descriptor (CTD).

@@

% cycle of operation
\begin{figure*}[ht!]
        \centering
        \includegraphics[height=3.0in]{figures/ch3/digram-project-cycle}
        \caption{This figure represents an operation cycle of SIMITAR, emphasizing each main step: sniffing, flow classification, data storing, data processing and fitting, model parameterization,  and synthetic traffic generation.}
    \label{fig:cycle-of-operation}
\end{figure*}

@@

% ok1

To meet the requirements presented in the chapter ~\ref{ch:introduction}, we will define our solution, and how it works. SIMITAR architecture is presented in the figure~\ref{fig:architecture}. It is composed of four components: a \textit{Sniffer}, a \textit{SQLite database}, a \textit{TraceAnalyzer}, a \textit{FlowGenerator};  and a \textit{Network Traffic Generator}, as subsystem. We describe each part below.

@@

% ok1

This component collects network traffic data and classifies it into flows, storing stores in an SQLite database. It defines each flow by the same criteria used by SDN switches\cite{sdn-survey},  through header fields matches. It uses:

\begin{itemize}
\item Link Protocol
\item Network Protocol
\item Network Source and Destination Address
\item Transport Protocol
\item Transport Source and Destination Port
\end{itemize}

@@

We implemented the first version of this component in Shell Script (Bash).  Tsahrk\footnote{\href{https://www.wireshark.org/docs/man-pages/tshark.html}{https://www.wireshark.org/docs/man-pages/tshark.html}} was used to extract header fields, and Awk to match the flows, and Sed/Awk to create the SQLite queries. This version was too slow to operate in real time on Ethernet interfaces. On the other hand, this approach was fast to implement and enable the implementation of the other components. The second and current version was made using Python. This version used Pyshark \footnote{\href{https://pypi.python.org/pypi/pyshark}{https://pypi.python.org/pypi/pyshark}} as sniffer library.

It has a data structure we developed called \textit{OrderedSet}. A set is a list of elements with no repetition but does not keep track of the insertion order. Our OrderedSet does. Also, it makes use of a  64 bits hash function of the family FNV\footnote{The collision probability of a good 64 bits hash function in a table with 10000 items is about of $2.71e-12$.}. The listed header fields are inputs for a hash function, and its value is set on the ordered set which returns its order (index on the \textit{OrderedSet}). The index value is chosen as a packet flowID.

%c++ http://ideone.com/F0V42m
As future improvements for this component, we propose a more efficient implementation in C++ and data visualization for the collected data. In that way, we may optimize the packet processing. We discuss this in deeper details in the chapter~\ref{ch:conclusion}.

@@

% ok1

The database stores the collected raw data from the traces for further analysis. The \textit{Sniffer} and the \textit{TraceAnalyzer} components uses the database.  We choose an SQLite database, because according to its specifications\footnote{\href{https://www.sqlite.org/whentouse.html}{https://www.sqlite.org/whentouse.html}}, it fits well our purposes. It is simple and well-suitable for an amount of data smaller than terabytes. In the figure ~\ref{fig:simitar-database} we present the relational model of our database, which stores a set of features extracted from packets, along with the flowID calculated by the sniffer component.

@@

% ok1

This module is the core of our project. It creates a trace model via the analysis of the collected data. We define here a Compact Trace Descriptor (CTD) as a human and machine-readable file, which describes a traffic trace through a set of flows, each of them represented by a set of parameters, such as header information and analytical models.  The Trace Analyze has the task to learn these features from raw traces data (stored in the SQLite database) and generate an XML file.  In the figure~\ref{fig:CTD-diagram} we show a directory diagram of a CDT file. It has many of many flow fields, and each one contains each parameter estimated. Now we will describe how we construct it.

@@

\subsubsection{Flow features}

% ok1

Some unique per-flow features are directly measured from the data. They are:

@@

\subsubsection{Inter Packet Times}

@@

To represent inter-packet times, we adopt a simplified version of the Harpoon's traffic model. A deep explanation of the original model can be found at \cite{harpoon-paper} and \cite{harpoon-validation}. Here, we will explain our simplified version, which is illustrated at figure~\ref{fig:modified-harpoon-model}.

Harpoon uses a definition of each level, based on the measurement of SYN and ACK TCP flags. It uses TCP flags (SYN) to classify packets in different levels, named their file, session, and user level. We choose to estimate these values, based on inter-packet times only. The distinction is made based on the time delay between packets.

In our algorithm simplified version, we define three different layers of data transference to model and control: file, session, and flow. For SIMITAR, a file is just a sequence of consecutive packets transmitted continuously, without large interruption of traffic. It can be, for example, packets sent downloading a file, packets from a  UDP  connection or a single ICMP echo packet. The session-layer refers to a sequence of multiple files transmitted between a source and a destination, belonging to the same flow.  The flow level refers to the conjunct of flows, as classified by the Sniffer.  Now, we explain SIMITAR operation on each layer.

In the \textbf{flow layer} the \textit{TraceAnalyzer} loads the flow arrival times from the database and calculates the inter-packet times within the flow context.

At the \textbf{session layer}, we use a deterministic approach for evaluating file transference time and times between files: ON/OFF times sequence of packet trains. We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.  We develop an algorithm called \textit{calcOnOff} responsible for estimating these times. It also determines the number of packets and bytes transferred by each file. Since the ON times will serve as input for actual traffic generators, we defined a minimum acceptable time for on periods equals to 100 ms. ON times can be arbitrary smalls, and they could be incompatible with acceptable ON periods for traffic generators. Also in the case of just one packet, the ON time would be zero. So setting a minimum acceptable time to solve these issues. The OFF times, on the other hand, are defined by the constant \texttt{session\_cut\_time} \footnote{In the code it is called \texttt{DataProcessor::m\_session\_cut\_time} }. If the time between two packets of the same flow is larger than \texttt{session\_cut\_time}, we consider them belonging to a different file, so this time is a session OFF time. In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} for the \texttt{session\_cut\_time}: 30 seconds. The control of ON/OFF periods in the traffic generation is made by the \textit{Flow Generator} component \footnote{This control is made by the class \texttt{NetworkFlow}}.

In the \textbf{file layer}, we model the inter-packet times at the file level. To estimate inter-packet times within files, we select all inter-packet times smaller than \texttt{session\_cut\_time}\footnote{In the code it is called\texttt{DataProcessor::m\_session\_cut\_time} }. All files within the same flow are considered to follow the same model. We delegate the control of the inter-packet times to the underlying workload engine tool. We ordered them, from the best to the worst. Currently, we are using eight different stochastic functions parameterizations. They are Weibull(linear regression), Normal(mean/standard deviation calculation), Exponential(mean and linear regression estimation), Pareto(linear regression and maximum likelihood), Cauchy(linear regression) and Constant(mean calculation). From those, Weibull, Pareto, and Cauchy are heavy-tailed functions, and therefore self-similar processes. But if the flow has less than 30 packets, just the constant model is evaluated. It is because numerical methods gave poor results if the data sample used is small. We sort these models according to the Akaike Information Criterion (AIC) as default\cite{sourcesonoff-paper}\cite{bic-aic-comparision}. We will enter into deeper details on this methodology on the chapter ~\ref{ch:modeling-evaluation}. The methodology of selection is presented in the figure~\ref{fig:model-parameterization}, and all constants and modes of operation can be changed by command line options.

\begin{figure*}[ht!]
    \centering
    \includegraphics[height=0.9in]{figures/ch3/simitar-parametrization}
    \caption{Diagram of parameterization and model selection for inter-packet times and inter-file times.}
    \label{fig:model-parameterization}
\end{figure*}

@@

Our approach for the packet size is much simpler. Since the majority of packet size distribution found on real measurements are bi-modal \cite{packet-distribution-model}\cite{sourcesonoff-paper}\cite{udp-flows-model}, we first sort all packet sizes of flow in two modes. We define a packet size mode cut value of 750 bytes, same value adopted by \cite{udp-flows-model}.

We know how much packets each mode has, and then we fit a model for it. We use three stochastic models: constant, exponential and normal. Since self-similarity does not make sense for packet-sizes, we prefer to use just the simpler models. When there is no packet for a model, we set a flag NO\_MODEL, and when there is just a single packet we just use the constant model. Then calculate the BIC and AIC for each, but we decide to set the constant model as the first.

As is possible to see in many works \cite{packet-distribution-model} \cite{udp-flows-model}, since the standard deviation of each mode tends to be small, constant fittings use to give good approximations. Also, it is computationally cheaper for the traffic generated than the other models, since no calculation is a need for each packet sent. Since both AIC and BIC criteria always will select the constant model as the worst, we decide to ignore this.

@@

We first implemented it using the D-ITG API. But our Flow Generator can use any traffic generator with API, CLI or script interface as well. To easily expand this component, we use the design pattern factory. If the user wants to introduce support for a new traffic generator, he just has to expand the class \texttt{DummyFlow} and add the support on the method \texttt{make\_flow()} of the class \texttt{NetworkFlow}. We will discuss this deeper in the next section.

This component works in two different layers according to the traffic generators classification introduced in the chapter ~\ref{ch:literature-review}: at the Flow level, and packet level, as presented in the figure ~\ref{fig:layers-workload-tools}.

@@

At the flow-level, it controls each flow using the algorithm at figure~\ref{alg-simplified-harpoon}. This algorithm handles our model defined at the figure~\ref{fig:modified-harpoon-model}.

%2nd-review
It starts a \textit{thread} for each flow in the \textit{Compact Trace Descriptor}, then the thread sleeps its \texttt{start\_delay}. It is the time when the first flow packet was captured in the original capture. It then calls the underlying traffic generation method, passing to it the file ON time, number of packets and number of bytes to be sent (file size). Then it sleeps the next session OFF time from the stack until it ends. When the list of ON/OFF times is over, the thread ends.

@@

%2nd-review
At the packet level, it must use the expanded class of the \texttt{DummyFlow}. In this level, the job of our tool is to configure the underlying engine, to send a file, as defined before. Therefore it uses the \textit{getters} available, and the passed parameters, defined by the operation described in the previous session. The implementation of this level should follow the flowchart presented in the figure ~\ref{fig:alg-traffic-engine-config}.
Down below we present a simplistic code of how the D-ITG API can be used to generate packet-level traffic. We call this concept \textit{Flow Generation Programming} A more complex configuration is possible, but it serves to illustrate the procedure. Its API documentation is available at on D-ITG web-site \footnote{\href{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}{http://www.grid.unina.it/software/ITG/manual/index.html\#SECTION00047000000000000000}}. 
\begin{minted}[frame=single,
               framesep=3mm,
               linenos=true,
               xleftmargin=21pt,
               tabsize=4,
               fontsize=\scriptsize, 
               breaklines=true]{c++}
void flowGenerate(const counter& flowId, const time_sec& onTime, const uint& npackets, const uint& nbytes,  const string& netInterface)
{
	char localhost[CHAR_BUFFER];
	string strCommand;
	char command[CHAR_BUFFER];
	uint i = 0;
	int rc = 0;
	getLocalIp("eth0", localhost);
	strCommand += " -t " + std::to_string(onTime); 
	strCommand += " -k " + std::to_string(nbytes / 1024);
	strCommand += " -a " + getHostIP();
	if (this->getTransportProtocol() == PROTOCOL__TCP)
		strCommand += " -T TCP -D ";
	else if (this->getTransportProtocol() == PROTOCOL__UDP)
		strCommand += " -T UDP ";
	else if (this->getTransportProtocol() == PROTOCOL__ICMP)
		strCommand += " -T ICMP ";
	for(;;i++)
	{	
		StochasticModelFit idtModel = this->getInterDepertureTimeModel(i);
		if(idtModel.modelName() == WEIBULL)
		{
			strCommand += " -W " + std::to_string(idtModel.param1()) + " " + std::to_string(idtModel.param2());
			break;
		}
		else if ( idtModel.modelName() == CONSTANT)
		{
			strCommand += " -C " + std::to_string(nbytes/(1024*onTime));
			break;
		}
	}
	strcpy(command, strCommand.c_str());
	rc = DITGsend(localhost, command); // it is not blocking
    usleep(onTime*10e6);
	if (rc != 0)
	{
		printf("\nDITGsend() return value was %d\n", rc);
		exit(EXIT_FAILURE);
	}
}
\end{minted}
